Automated Verification of Stand-Alone Solar Photovoltaic Systems

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
updated references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
Related to solar PV systems, the project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.  
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to formally verify a PV system as an imperative program.

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by software simulation tools using \textcolor{blue} {MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}}, or HOMER Pro \cite{Lamnadi2017}. Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids. 
%
In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
Given the current knowledge in formal verification, this is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, this paper makes three original contributions. Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into first-order theories supported by software model checkers. Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT). Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other state-of-the-art approaches based on simulation.

>>>>

%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically, 
Related to solar PV systems, the project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements or whether it will fail due to weather conditions, which aids to improve the project itself.  
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}. Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids. 
%
In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
Given the current knowledge in formal verification, this is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, this paper makes three original contributions. Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT). Thirdly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other state-of-the-art approaches based on simulation.
